---
title: "Daughters"
author: "Enxhi Buxheli and John LaVelle"
date: "2/2/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment=NA)

# Attaching necessary libraries
library(tidyverse)
library(dplyr)
library(janitor)
library(knitr)
library(kableExtra)

# Attaching necessary libraries from replication code
library(xtable)
library(stargazer)


## The below are global options used to clean up the formatting and 
## overall appearance of the code.

# Global option used in table to replace NAs with '-' for aesthetics
options(knitr.kable.NA = '-')
# Global option used in creating tables to get rid of junk output
options(xtable.comment = FALSE)
```


```{r xtable, results="asis"}

# Creating judge and case data to be used for tables in the replication.
# clean_names() is not necessary, but was added to ensure that there were no improperly
# formatted variable names that could result in errors when running the code. Better safe
# than sorry!
case_data  <- read_csv("dataverse_files/glynn_sen_daughters_by_case_1.csv") %>% clean_names()
judge_data <- read_csv("dataverse_files/glynn_sen_daughters_by_judge.csv") %>% clean_names()
           

########################################################
## Loading the Data [code below was taken from replication data]
########################################################

## This loads three data sets
## 1. Gender cases
## 2. Cleaned by-judge data
## 3. Non-gender cases, downloaded from Kuersten and Haire's website
## (Commented out; their data are available from their website)

# ## Gender cases only
# ## Removing male plaintiffs and making variables readable
women_cases <- subset(case_data, femplaintiff == 1)
women_cases <- subset(women_cases, 
                      (area %in% c("employment", "Title IX", "pregnancy", 
                                   "abortion", "reproductive rights")))
women_cases$area <- factor(women_cases$area, 
                           levels = c("abortion","employment","pregnancy",
                                      "reproductive rights","Title IX"))

# subsets judge data to those for whom we have fertility data
all <- filter(judge_data, !is.na(girls))
```

# Table 2: Demographics of U.S. Courts of Appeals Judges Who Voted on Gender-Related Cases, 1996-2002
```{r, results="asis"}
########################################################
## Table 2: Judge Demographics
########################################################

# creating subsets of the original data set for further analysis
dems  <- subset(all, republican == 0)
reps  <- subset(all, republican == 1)
women <- subset(all, woman == 1)
men   <- subset(all, woman == 0)

mean_kids <-  tibble(all = mean(na.omit(all$child)), 
                     dems  = mean(na.omit(dems$child)),
                     reps  = mean(na.omit(reps$child)),
                     women = mean(na.omit(women$child)),
                     men   = mean(na.omit(men$child)))

mean_girls <-  tibble(all = mean(na.omit(all$girls)), 
                      dems  = mean(na.omit(dems$girls)),
                      reps  = mean(na.omit(reps$girls)),
                      women = mean(na.omit(women$girls)),
                      men   = mean(na.omit(men$girls)))

# frequency tables for children
aa <- table(na.omit(all$child))   #all
bb <- table(na.omit(dems$child))  #dems
cc <- table(na.omit(reps$child))  #reps
dd <- table(na.omit(women$child)) #women
ee <- table(na.omit(men$child))   #men

# proportions for 
plus6_all   <- sum(aa[7:length(aa)])/sum(aa)
plus6_dems  <- sum(bb[7:length(bb)])/sum(bb)
plus6_reps  <- sum(cc[7:length(cc)])/sum(cc)
plus6_women <- sum(dd[7:length(dd)])/sum(dd)
plus6_men   <- sum(ee[7:length(ee)])/sum(ee)
	
prop_six_or_greater <- tibble(all   = plus6_all, 
                              dems  = plus6_dems, 
                              reps  = plus6_reps, 
                              women = plus6_women, 
                              men   = plus6_men)

# Creates a tibble for the specified index to output a 
# proportions table
prop <- function(index){
  tibble(all   = sum(aa[index])/sum(aa), 
         dems  = sum(bb[index])/sum(bb), 
         reps  = sum(cc[index])/sum(cc),
         women = sum(dd[index])/sum(dd), 
         men   = sum(ee[index])/sum(ee))
}

# creating the tibble outputs for the prop tables
prop_zero  <- prop(1)
prop_one   <- prop(2)
prop_two   <- prop(3)
prop_three <- prop(4)
prop_four  <- prop(5)
prop_five  <- prop(6)
	
mean_female <- tibble(all   = mean(na.omit(all$woman)), 
                      dems  = mean(na.omit(dems$woman)),
                      reps  = mean(na.omit(reps$woman)),
                      women = NA_character_, #perfectly correlated (placeholder for Women)
                      men   = NA_character_  #perfectly correlated (placeholder for Men)
)

mean_rep <- tibble(all   = mean(na.omit(all$republican)), 
                   dems  = NA_character_, #perfectly correlated (placeholder for Democrats)
                   reps  = NA_character_, #perfectly correlated (placeholder for Republicans)
                   women = mean(na.omit(women$republican)),
                   men   = mean(na.omit(men$republican))
)

mean_white <- tibble(all   = mean(na.omit(all$race == 1)), 
                     dems  = mean(na.omit(dems$race == 1)),
                     reps  = mean(na.omit(reps$race == 1)), 
                     women = mean(na.omit(women$race == 1)),
                     men   = mean(na.omit(men$race == 1))
)

mean_yearb <- tibble(all   = mean(na.omit(all$yearb)), 
                     dems  = mean(na.omit(dems$yearb)),
                     reps  = mean(na.omit(reps$yearb)), 
                     women = mean(na.omit(women$yearb)),
                     men   = mean(na.omit(men$yearb))
)

no_judges <- tibble(all   = nrow(all), 
                    dems  = nrow(dems), 
                    reps  = nrow(reps), 
                    women = nrow(women), 
                    men   = nrow(men))

demographic_table <- rbind(mean_kids, mean_girls, 
                           prop_zero, prop_one,prop_two, prop_three, prop_four, prop_five,
                           prop_six_or_greater, 
                           mean_female, mean_rep, mean_white, mean_yearb, no_judges) %>% 
  mutate(all   = as.numeric(all),
         dems  = as.numeric(dems),
         reps  = as.numeric(reps),
         women = as.numeric(women),
         men   = as.numeric(men))

rownames(demographic_table) <- c("Mean Number of Children", "Mean Number of Girls",
	"Proportion Who Have 0 Children","1 Child",
	"2 Children", "3 Children",
	"4 Children", "5 Children", "6 Children or More", "Proportion Female", "Proportion Republican",
	"Proportion White", "Mean Year Born", "N")

# creating nicely formatted table
demographic_table %>% 
  kable(booktabs = TRUE, digits = 2,
        col.names = c("All", "Democrats", "Republicans","Women", "Men")) %>% 
  kable_styling(position = "center")
```


```{r}
########################################################
## Calculating the Weights (Number of Cases)
########################################################

no_cases <- matrix(data = NA, nrow = nrow(judge_data), ncol = 1)
for(i in 1:length(no_cases)){
	no_cases[i] <- nrow(women_cases[which(women_cases$name == judge_data$name[i]),])
	}

judge_data <- cbind(judge_data, no_cases)

## total number of cases we are working with

########################################################
## Calculating the Outcome Var
########################################################

no_liberalvote <- matrix(data = NA, nrow = nrow(judge_data), ncol = 1)
for(i in 1:length(no_liberalvote)){
	stuff <- women_cases[which(women_cases$name == judge_data$name[i]),]
	no_liberalvote[i] <- nrow(subset(stuff, vote == 2 | vote == 3))
	}

lib_vote_share <- no_liberalvote/no_cases

judge_data <- cbind(judge_data, no_liberalvote, lib_vote_share)
judge_data <- subset(judge_data, girls != "NaN")

########################################################
## Subsetting Data to Various Populations (for use later)
########################################################

## just women:
women_means <- subset(judge_data, woman == 1)

## just men:
men_means <- subset(judge_data, woman == 0)

## just republicans:
rep_means <- subset(judge_data, republican == 1)

## just democrats
dem_means <- subset(judge_data, republican == 0)

## for example, this code is used in Figure 1, table 3

```

\newpage
# Table 3: Distribution of the Number of Gender-Related Cases Heard per Judge, 1996-2002
```{r, results="asis"}
#######################################################
## Table 3: Distribution of Cases
########################################################

# binding summary statistics for different parties
gg <- rbind(summary(judge_data$no_cases), 
            summary(dem_means$no_cases), 
            summary(rep_means$no_cases))

# making party names more aesthetically pleasing
rownames(gg) <- c("All Judges", "Democrats", "Republicans")

# feeding the results into a table
gg %>% 
  kable(digits = 2, booktabs = TRUE) %>% 
  kable_styling(position = "center")
```


\newpage

"Weighted least squares results, gender cases only. Outcome is proportion of feminist votes.  Models 1--4 are for all judges, while Models 5--8 are for judges with 1--4 children.  (No judge among those with 1--4 children had four girls.) All models include fixed effects for number of children and use weights based on the number of cases heard by each judge."


# Table 4: Weighted Least Squares Results, Gender-Related Cases Only
```{r stargazer, results="asis"}
########################################################
## Table 4: Core Results (WLS) 
########################################################

## Note from John: had to change as.factor(circuit.1) to as.factor(circuit_1), 
# because of the way that Zelig changed how they handle renaming columns
# with the same name

################ Results for all judges

mod_1 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

mod_2 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

mod_3 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = judge_data, weights = judge_data$no_cases)

mod_4 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = judge_data, weights = judge_data$no_cases)
		
################ Results for judges between 1 and 4 children
	
mod_5 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

mod_6 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

mod_7 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

mod_8 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])


cat("\\setcounter{table}{3}")
stargazer(mod_1, mod_2, mod_3, mod_4, mod_5, mod_6, mod_7, mod_8, 
          header = FALSE, style = "apsr", omit.stat = c("f","ser"),  font.size = "small",
          column.sep.width = "-8pt", digits = 2, 
          omit = c("circuit"), #line to omit descriptors
          dep.var.labels=c("All Judges","Judges with 1-4 Children"), #attempt at grouping columns
          keep = c("girls", "republican", "age", "religion", "woman", "race", "coefficients"),
          covariate.labels = c("1 Girl","2 Girls","3 Girls","4 Girls","5 Girls",
                               "At Least 1 Girl",	
                               "Republican","Age at Investiture","Catholic",
                               "Woman","African American","Hispanic",
                               "Constant"))
```

\newpage

"Logit and ordered logit results, gender cases only. Outcome is whether judge in a case votes in a feminist direction (Columns 1--5) or in a conservative, moderate, or liberal direction (Column 6).  All models include fixed effects for total number of children and Columns 3--6 include circuit and year fixed effects. Column 5 additionally includes standard errors clustered at the case level

# Table 5: Logit and Ordered Logit Results, Gender-Related Cases Only
```{r, results="asis"}
#######################################################
## Table 5: Core Results (Case-Level)
#######################################################

# DO ALL EXCEPT COLUMN 6 OF THIS ONE

# it seems like Mark suggested that we do this one using the built in 
# packages, instead of using this Zelig code.


wom_cases <- case_data %>% filter(femplaintiff == 1, area %in% c("employment", "Title IX", "pregnancy", "abortion", "reproductive rights"), child < 5 & child > 0) %>% 
  mutate(area = factor(area, c("abortion", "employment", "pregnancy", "reproductive rights", "Title IX")))


mod_7 <- glm(progressive_vote ~ as.factor(girls) + as.factor(child), data = wom_cases, family = binomial)
mod_8 <- glm(progressive_vote ~ I(girls > 0) + as.factor(child), data = wom_cases, family = binomial)
mod_9 <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit) + as.factor(year), data = wom_cases, family = binomial)
mod_10 <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = wom_cases, family = binomial)
my.out11 <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = wom_cases, family = binomial)

## Now: Calculating standard errors bootstrapped at the case level:
## Note: This takes about 10 minutes to run. 

## Grab the data for these two models
mod11 <- as.formula("~ progressive_vote + vote + girls +  child + republican +race + age + religion + woman + circuit + year + area + casename")

dat11 <- model.frame(mod11, data = subset(women_cases, child < 5 & child > 0))
dat11$casename <- as.character(dat11$casename)

## Create list of data.frames for each case for easy reference
casenames <- sort(unique(dat11$casename))
caselist <- lapply(casenames, function(x) dat11[which(dat11$casename == x),])
names(caselist) <- casenames


# in order to run the bootstrap algo, you need to uncomment out from "Running the bootstraps" to "End Bootstrap code here"

# otherwise you can just used the saved data

# # Running the bootstraps
# # Note that not all of the coefficients will be sampled in any given of the
# # bootstraps - this might result in some warnings form polr
# # (the ordered logit), but is not a problem for the results
# boots <- 1000
# b.star11 <- matrix(NA, ncol = length(list("(Intercept)",        "I(girls > 0)TRUE", "as.factor(child)2"   , "as.factor(child)3"   ,
# "as.factor(child)4"        ,          "republican"           ,
#  "age"                             ,   "I(religion == 4)TRUE"          ,
#  "woman"                ,              "I(race == 2)TRUE"             ,
#  "I(race == 3)TRUE"               ,    "as.factor(circuit)10"          ,
#  "as.factor(circuit)11"           ,    "as.factor(circuit)2"          ,
#  "as.factor(circuit)3"             ,   "as.factor(circuit)4"             ,
# "as.factor(circuit)5"              ,  "as.factor(circuit)6"            ,
#  "as.factor(circuit)7"               , "as.factor(circuit)8"           ,
#  "as.factor(circuit)9"      ,          "as.factor(circuit)DC"         ,
# "as.factor(year)1997"       ,         "as.factor(year)1998"         ,
#  "as.factor(year)1999"        ,        "as.factor(year)2000"        ,
#  "as.factor(year)2001"         ,       "as.factor(year)2002"       ,
# "as.factor(area)employment"    ,      "as.factor(area)pregnancy" ,
#  "as.factor(area)reproductive rights", "as.factor(area)Title IX" )), nrow = boots)
# colnames(b.star11) <- list("(Intercept)",        "I(girls > 0)TRUE", "as.factor(child)2"   , "as.factor(child)3"   ,
# "as.factor(child)4"        ,          "republican"           ,
#  "age"                             ,   "I(religion == 4)TRUE"          ,
#  "woman"                ,              "I(race == 2)TRUE"             ,
#  "I(race == 3)TRUE"               ,    "as.factor(circuit)10"          ,
#  "as.factor(circuit)11"           ,    "as.factor(circuit)2"          ,
#  "as.factor(circuit)3"             ,   "as.factor(circuit)4"             ,
# "as.factor(circuit)5"              ,  "as.factor(circuit)6"            ,
#  "as.factor(circuit)7"               , "as.factor(circuit)8"           ,
#  "as.factor(circuit)9"      ,          "as.factor(circuit)DC"         ,
# "as.factor(year)1997"       ,         "as.factor(year)1998"         ,
#  "as.factor(year)1999"        ,        "as.factor(year)2000"        ,
#  "as.factor(year)2001"         ,       "as.factor(year)2002"       ,
# "as.factor(area)employment"    ,      "as.factor(area)pregnancy" ,
#  "as.factor(area)reproductive rights", "as.factor(area)Title IX" )
# 
# set.seed(1234)
# for (b in 1:boots) {
# 	clust.sample <- sample(casenames, replace = TRUE)
# 	c.boot <- do.call(rbind,lapply(clust.sample,function(x) caselist[[x]]))
# 	out11.star <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican
# 	+ age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = c.boot, family = binomial("logit"))
# 	  b.star11[b,names(out11.star$coef)] <- out11.star$coef
# 	  # b.star11[b,names(out11.star$coef)] <- out11.star$coef
# 		}
# bcse11 <- apply(b.star11, 2, sd, na.rm=TRUE)
# save(list=c("bcse11"), file = "bootstraps.RData")

## End bootstrap code here


## can re-load bootstraped data to avoid having to run previous code
load("bootstraps.RData")

# todo: fix the constant row of this table

## Replacing the normal SEs with the bootstrap SEs for the final Table 5
stargazer(mod_7, mod_8, mod_9, mod_10, my.out11, header = FALSE, font.size = "small", type = "latex",
	 style = "apsr", omit.stat = c("f","ser"), 
	 keep = c("girls", "republican", "age", "religion", "woman", "race", "area", "coefficients"),
	 covariate.labels = c("1 Girl","2 Girls","3 Girls","At Least 1 Girl","Republican","Age at Investiture","Catholic","Woman","African American","Hispanic", "Employment", "Pregnancy", "Reproductive", "Title IX"),
se = list(mod_7 = NULL, mod_8 = NULL, mod_9 = NULL, mod_10 = NULL, my.out11 = bcse11), digits = 2)



```

\newpage
# Table 6: omitted from results

# Table 7: Weighted Least Squares Results
```{r, results="asis"}
########################################################
## Table 7: Dividing Up the Sample
########################################################

## First, limiting sample space to only judges 
## with 1-4 kids 
#(there is only 1 judge with no girls conditional on 5 or more kids)

rep_means <- subset(rep_means, child < 5 & child > 0)
dem_means <- subset(dem_means, child < 5 & child >0)
men_means <- subset(men_means, child < 5 & child > 0)
women_means <- subset(women_means, child < 5 & child > 0)

## and then by case
rep_cases <- subset(women_cases, child < 5 & child > 0 & republican == 1)
dem_cases <- subset(women_cases, child < 5 & child > 0 & republican == 0)
men_cases <- subset(women_cases, woman == 0)
womyn_cases <- subset(women_cases, woman == 1)


################ Party

mod_PARTY <- lm(lib_vote_share ~ I(girls > 0)*republican + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

## for republicans

mod_REP <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = rep_means, weights = rep_means$no_cases)

## for democrats

mod_DEM <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = dem_means, weights = dem_means$no_cases)

################ Gender

## for men
	
mod_GENDER <- lm(lib_vote_share ~ I(girls > 0)*woman + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

## for men
mod_MEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = men_means, weights = men_means$no_cases)

## for women
mod_WOMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = women_means, weights = women_means$no_cases)

mod_REPMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = subset(men_means, republican == 1), weights = men_means$no_cases[which(men_means$republican == 1)])

cat("\\setcounter{table}{6}")
stargazer(mod_REP, mod_DEM, mod_MEN, mod_WOMEN, mod_REPMEN,
	style = "ajps", header = FALSE, omit.stat = c("f","ser"), dep.var.labels = "Share of Votes in Feminist Direction", digits = 2, covariate.labels = c("At Least 1 Girl", "2 Children", "3 Children", "4 Children","Constant"), title = "Weighted least squares results. Outcome is judges' proportion of feminist votes on gender-related cases. All models include fixed effects for total number of children and use weights based on the number of cases heard by each judge.", label = "t:results_party")

```

\newpage
# Table 8
```{r, results="asis"}


########################################################
## Table 8: Judges with 0 or 1 child
########################################################

## Including people who have zero children as a control 
## suggested by AJPS editor 
## (Note: Caution against making inferences on effect of
## daughters among people with 0 children)

mod_12 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = subset(judge_data, child < 2), 
		weights = judge_data$no_cases[which(judge_data$child < 2)])
# summary(my.out12)

mod_13 <- lm(lib_vote_share ~ I(girls > 0), 
	data = subset(judge_data, child == 1), 
		weights = judge_data$no_cases[which(judge_data$child == 1)])
# summary(my.out13)

## and then controlling for rep or dem:

mod_14 <- lm(lib_vote_share ~ I(girls > 0) + I(republican==1), 
	data = subset(judge_data, child == 1), 
		weights = judge_data$no_cases[which(judge_data$child == 1)])
# summary(my.out14)


stargazer(mod_12, mod_13, mod_14, header = FALSE, 
	style = "ajps", omit.stat = c("f","ser"), dep.var.labels = "Liberal Judge-Vote",
	covariate.labels = c("1 Girl", "1 Child", "Republican", "Constant"))
```
\newpage
# Table 9: Proportion of Girls (Conditional on Number of Children) for U.S. Courts of Appeals Judges Participating in Gender-Related Cases, 1996-2002
```{r, results="asis"}

########################################################
## Table 9: Distribution of gender-related cases
########################################################


## just republicans:
rep_means <- subset(judge_data, republican == 1)

## just democrats
dem_means <- subset(judge_data, republican == 0)



aa <- table(dem_means$child, dem_means$girl)

bb <- table(rep_means$child, rep_means$girl)


aa_1 <- prop.table(table(dem_means$child, dem_means$girl),1)
bb_1 <- prop.table(table(rep_means$child, rep_means$girl),1)

colnames(aa_1) <- c("0 Girls", "1 Girl", "2 Girls", "3 Girls", "4 Girls", "5 Girls")

colnames(bb_1) <- c("0 Girls", "1 Girl", "2 Girls", "3 Girls", "4 Girls")

xtable(cbind(aa_1, bb_1))
```

# REMOVED TABLES:
# Table 1: Number of Children and Girls for U.S. Courts of Appeals Judges Participating in Gender-Related Cases, 1996-2002
```{r, results="asis"}
######################################################
## Table 1: Number of children and girls
######################################################

# Table 1: Number of Children and Girls for U.S. Courts of Appeals Judges 
#          Participating in Gender-Related Cases, 1996-2002
# Here we are keeping the # of children, # of girls, & party affiliation and
# building a count table. Additionally, here the party name is recoded to be
# more friendly to a reader of the table ("Republicans" and "Democrats")
t1 <- select(judge_data,
              child, girls, republican) %>% 
  filter(child < 10, girls < 10) %>% 
  mutate(party = ifelse(1 == republican, "Republicans", "Democrats"))


# Number of Children portion of the table
t1_child <- t1 %>% 
  count(party, child) %>% 
  spread(child, n) %>% 
  adorn_totals("col")

# Number of Girls portion of the table
t1_girls <- t1 %>% 
  count(party, girls) %>% 
  spread(girls, n) %>% 
  adorn_totals("col")

# Binding the rows to create one table with girls and children
# column_spec is a function that adds the row with the total counts
t1_combined <- bind_rows(t1_child, t1_girls)
colnames(t1_combined) <- c("Count", "0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "N")
t1_combined %>% 
  kable("latex", booktabs = TRUE, col.names = ) %>% kable_styling(position = "center") %>% 
  column_spec(1, bold = TRUE) %>% 
  group_rows("Number of Children", 1, 2, bold = TRUE) %>% 
  group_rows("Number of Girls", 3, 4, hline_before = TRUE)
```

## Figure 1: Distribution of the Proportion of Cases Decided in a Feminist Direction out of All Gender-Related Cases Decided, 1996-2002
```{r}
#######################################################
## Figure 1
########################################################

plot(density(judge_data$lib_vote_share), 
	xlim = c(-.4,1.4), ylim = c(0,2.5),
	ylab = "", xlab = "Proportion of Cases Decided in a Feminist Direction", 
	yaxt = "n", 
	bty = "n", 
	main = "",
	col = "black", lwd = 2)
lines(density(rep_means$lib_vote_share), 
	col = "firebrick", lwd = 2, lty  = 2)
lines(density(dem_means$lib_vote_share), 
	col = "dodgerblue", lwd = 2, lty  = 3)
abline(v = .5, col = "grey50", lty = 2)
text(x = .5, y = 2.4, "Less Feminist", col = "grey50", pos = 2, cex = 0.9)
text(x = .5, y = 2.4, "More Feminist", col = "grey50", pos = 4, cex = 0.9)
text(x = .25, y = 1.7, "Republicans", pos = 2, cex = 0.9)
text(x = .7, y = 1, "Democrats", pos = 4, cex = 0.9)
text(x = .075, y = .6, "All", pos = 4, cex = 0.9)

```
