---
title: "Daughters"
author: "Enxhi Buxheli and John LaVelle"
date: "2/2/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment=NA)

# Attaching necessary libraries
library(tidyverse)
library(dplyr)
library(janitor)
library(knitr)
library(kableExtra)

# Attaching necessary libraries from replication code
library(xtable)
library(stargazer)


## The below are global options used to clean up the formatting and 
## overall appearance of the code.

# this is a good thing to do in general, nice

# Global option used in table to replace NAs with '-' for aesthetics
options(knitr.kable.NA = '-')
# Global option used in creating tables to get rid of junk output
options(xtable.comment = FALSE)
```

Definitely want a short abstract in the future 

```{r xtable, results="asis"}

# Creating judge and case data to be used for tables in the replication.
# clean_names() is not necessary, but was added to ensure that there were no improperly
# formatted variable names that could result in errors when running the code. Better safe
# than sorry!
case_data  <- read_csv("dataverse_files/glynn_sen_daughters_by_case_1.csv") %>% clean_names()
judge_data <- read_csv("dataverse_files/glynn_sen_daughters_by_judge.csv") %>% clean_names()

# good
           

########################################################
## Loading the Data [code below was taken from replication data]
########################################################

## This loads three data sets
## 1. Gender cases
## 2. Cleaned by-judge data
## 3. Non-gender cases, downloaded from Kuersten and Haire's website
## (Commented out; their data are available from their website)

# ## Gender cases only
# ## Removing male plaintiffs and making variables readable
women_cases <- subset(case_data, femplaintiff == 1)
women_cases <- subset(women_cases, 
                      (area %in% c("employment", "Title IX", "pregnancy", 
                                   "abortion", "reproductive rights")))
women_cases$area <- factor(women_cases$area, 
                           levels = c("abortion","employment","pregnancy",
                                      "reproductive rights","Title IX"))

# subsets judge data to those for whom we have fertility data
all <- filter(judge_data, !is.na(girls))
```

# Table 2: Demographics of U.S. Courts of Appeals Judges Who Voted on Gender-Related Cases, 1996-2002
```{r, results="asis"}
########################################################
## Table 2: Judge Demographics
########################################################

# creating subsets of the original data set for further analysis
dems  <- subset(all, republican == 0)
reps  <- subset(all, republican == 1)
women <- subset(all, woman == 1)
men   <- subset(all, woman == 0)

# frequency tables for children
aa <- table(na.omit(all$child))   #all
bb <- table(na.omit(dems$child))  #dems
cc <- table(na.omit(reps$child))  #reps
dd <- table(na.omit(women$child)) #women
ee <- table(na.omit(men$child))   #men

# Creates a tibble for the specified index to output a 
# proportions table
prop <- function(index){
  tibble(all   = sum(aa[index])/sum(aa), 
         dems  = sum(bb[index])/sum(bb), 
         reps  = sum(cc[index])/sum(cc),
         women = sum(dd[index])/sum(dd), 
         men   = sum(ee[index])/sum(ee))
}

# creating the tibble outputs for the prop tables for judges with 0-5 children
prop_zero  <- prop(1)
prop_one   <- prop(2)
prop_two   <- prop(3)
prop_three <- prop(4)
prop_four  <- prop(5)
prop_five  <- prop(6)

# proportions for those with greater than 5 children
plus6_all   <- sum(aa[7:length(aa)])/sum(aa)
plus6_dems  <- sum(bb[7:length(bb)])/sum(bb)
plus6_reps  <- sum(cc[7:length(cc)])/sum(cc)
plus6_women <- sum(dd[7:length(dd)])/sum(dd)
plus6_men   <- sum(ee[7:length(ee)])/sum(ee)

# putting it all together into 1 tibble
prop_six_or_greater <- tibble(all   = plus6_all, 
                              dems  = plus6_dems, 
                              reps  = plus6_reps, 
                              women = plus6_women, 
                              men   = plus6_men)

# Getting together the mean data from all of the data subsets. Tried to make
# it better looking by getting rid of the na.omit, but didn't want to mess up 
# the code.
mean_kids <-  tibble(all = mean(na.omit(all$child)), 
                     dems  = mean(na.omit(dems$child)),
                     reps  = mean(na.omit(reps$child)),
                     women = mean(na.omit(women$child)),
                     men   = mean(na.omit(men$child))
)
mean_girls <-  tibble(all = mean(na.omit(all$girls)), 
                      dems  = mean(na.omit(dems$girls)),
                      reps  = mean(na.omit(reps$girls)),
                      women = mean(na.omit(women$girls)),
                      men   = mean(na.omit(men$girls))
)
mean_female <- tibble(all   = mean(na.omit(all$woman)), 
                      dems  = mean(na.omit(dems$woman)),
                      reps  = mean(na.omit(reps$woman)),
                      women = NA_character_, #perfectly correlated (placeholder for Women)
                      men   = NA_character_  #perfectly correlated (placeholder for Men)
)
mean_rep <- tibble(all   = mean(na.omit(all$republican)), 
                   dems  = NA_character_, #perfectly correlated (placeholder for Democrats)
                   reps  = NA_character_, #perfectly correlated (placeholder for Republicans)
                   women = mean(na.omit(women$republican)),
                   men   = mean(na.omit(men$republican))
)
mean_white <- tibble(all   = mean(na.omit(all$race == 1)), 
                     dems  = mean(na.omit(dems$race == 1)),
                     reps  = mean(na.omit(reps$race == 1)), 
                     women = mean(na.omit(women$race == 1)),
                     men   = mean(na.omit(men$race == 1))
)
mean_yearb <- tibble(all   = mean(na.omit(all$yearb)), 
                     dems  = mean(na.omit(dems$yearb)),
                     reps  = mean(na.omit(reps$yearb)), 
                     women = mean(na.omit(women$yearb)),
                     men   = mean(na.omit(men$yearb))
)
no_judges <- tibble(all   = nrow(all), 
                    dems  = nrow(dems), 
                    reps  = nrow(reps), 
                    women = nrow(women), 
                    men   = nrow(men))

# binding all of the data together to make a table ready for output
demographic_table <- rbind(mean_kids, mean_girls, 
                           prop_zero, prop_one,prop_two, prop_three, prop_four, prop_five,
                           prop_six_or_greater, 
                           mean_female, mean_rep, mean_white, mean_yearb, no_judges) %>% 
  # this mutate statement became necessary when I was trying to round the numbers
  # for the final output of the table because the NAs cast the columns as non-numeric.
  # this mutate allows for kable to round properly to make the output look pretty
  mutate(all   = as.numeric(all),     
         dems  = as.numeric(dems),
         reps  = as.numeric(reps),
         women = as.numeric(women),
         men   = as.numeric(men))

rownames(demographic_table) <- c("Mean Number of Children", "Mean Number of Girls",
	"Proportion Who Have 0 Children","1 Child",
	"2 Children", "3 Children",
	"4 Children", "5 Children", "6 Children or More", "Proportion Female", "Proportion Republican",
	"Proportion White", "Mean Year Born", "N")
	
	# really nicely formatted table in the PDF, good job

# creating nicely formatted table
demographic_table %>% 
  kable(booktabs = TRUE, digits = 2,
        col.names = c("All", "Democrats", "Republicans","Women", "Men")) %>% 
  kable_styling(position = "center")
```


```{r}
########################################################
## Calculating the Weights (Number of Cases)
########################################################

no_cases <- matrix(data = NA, nrow = nrow(judge_data), ncol = 1)
for(i in 1:length(no_cases)){
	no_cases[i] <- nrow(women_cases[which(women_cases$name == judge_data$name[i]),])
	}

judge_data <- cbind(judge_data, no_cases)

## total number of cases we are working with

########################################################
## Calculating the Outcome Var
########################################################

# comments on what this is doing (besides calculating outcome var) would be good

no_liberalvote <- matrix(data = NA, nrow = nrow(judge_data), ncol = 1)
for(i in 1:length(no_liberalvote)){
	stuff <- women_cases[which(women_cases$name == judge_data$name[i]),]
	no_liberalvote[i] <- nrow(subset(stuff, vote == 2 | vote == 3))
	}

lib_vote_share <- no_liberalvote/no_cases

judge_data <- cbind(judge_data, no_liberalvote, lib_vote_share)
judge_data <- subset(judge_data, girls != "NaN")

########################################################
## Subsetting Data to Various Populations (for use later)
########################################################

## just women:
women_means <- subset(judge_data, woman == 1)

## just men:
men_means <- subset(judge_data, woman == 0)

## just republicans:
rep_means <- subset(judge_data, republican == 1)

## just democrats
dem_means <- subset(judge_data, republican == 0)

## for example, this code is used in Figure 1, table 3

```

\newpage
# Table 3: Distribution of the Number of Gender-Related Cases Heard per Judge, 1996-2002
```{r, results="asis"}
#######################################################
## Table 3: Distribution of Cases
########################################################

# binding summary statistics for different parties
gg <- rbind(summary(judge_data$no_cases), 
            summary(dem_means$no_cases), 
            summary(rep_means$no_cases))

# making party names more aesthetically pleasing
rownames(gg) <- c("All Judges", "Democrats", "Republicans")

# feeding the results into a table
gg %>% 
  kable(digits = 2, booktabs = TRUE) %>% 
  kable_styling(position = "center")
  
  # very nice table again
```

\newpage

# Table 4: Weighted Least Squares Results, Gender-Related Cases Only

This table deals with a regression of the percent increase in the likelihood of a judge deciding a case in the feminine (feminist) direction. The weights in the regression correspond to the number of cases that have been heard by each judge. This application in the paper makes sense, because it is desireable to assign more significance in our model to the data we are more sure is correct (in this case defined as having more observed occurences of a judge's behavior). 

However, there are concerns with the overall shape of the data. First, the data set contains a lot of very low numbers of cases - 50% of the judges have less than or equal to 8 cases that describe them, and 25% have less than or equal to 5 cases. On the low end, that means there are a lot of judges who have a very low numbers of cases we have data on. This means the proportion of progressive votes decided could be significantly inaccurate for many judges with very small case files. Because the model underweighs these areas of the data, however, the deletion of these potentially incorrect points should not affect the ultimate model. 

The algorithm also very heavily weights cases with a significant amount of data. However, because there are very few of these cases, the potentially outlying statistical effects can be greatly increased. One interesting artifact of their removal, however, is the significance of some the factors increases slightly. It is possible that this is due to some significant outliers in the dataset from the weighted method used to compute the regression.

The main motivation for this analysis in table 4 is the realization that there are many low case counts for many judges, which potentially results in a significant discrepancy or error interval surrounding their empirically observed proportion of votes cast in a feminist manner. For example, using a Bayesian and binomial interpretation of the proportion of votes cast in a feminist manner, a judge with only four data points informing an estimate of his or her likelihood to vote would have a large error interval.

It should be recognized that the quality and estimation of this data is of the utmost importance. If the predictor is biased towards using the data of a a small number of judges, then the the model may not generalize sufficiently to other cases.

Excellent, clear, and thorough description, this is great and shows me how you're thinking through the choices made by the authors


\newpage

"Weighted least squares results, gender cases only. Outcome is proportion of feminist votes.  Models 1--4 are for all judges, while Models 5--8 are for judges with 1--4 children.  (No judge among those with 1--4 children had four girls.) All models include fixed effects for number of children and use weights based on the number of cases heard by each judge."




# Table 4: Weighted Least Squares Results, Gender-Related Cases Only
```{r stargazer, results="asis"}
########################################################
## Table 4: Core Results (WLS) 
########################################################

## Note from John: had to change as.factor(circuit.1) to as.factor(circuit_1), 
# because of the way that Zelig changed how they handle renaming columns
# with the same name

################ Results for all judges

mod_1 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

mod_2 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

mod_3 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = judge_data, weights = judge_data$no_cases)

mod_4 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = judge_data, weights = judge_data$no_cases)
		
################ Results for judges between 1 and 4 children
	
mod_5 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

mod_6 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

mod_7 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

mod_8 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = subset(judge_data, child < 5 & child > 0), weights = judge_data$no_cases[which(judge_data$child > 0 & judge_data$child < 5)])

# see https://www.jakeruss.com/cheatsheets/stargazer/#labelling-the-table for how to caption the table with stargazer

cat("\\setcounter{table}{3}")
stargazer(mod_1, mod_2, mod_3, mod_4, mod_5, mod_6, mod_7, mod_8, 
          header = FALSE, style = "apsr", omit.stat = c("f","ser"),  font.size = "small",
          column.sep.width = "-8pt", digits = 2, 
          omit = c("circuit"), #line to omit descriptors
          dep.var.labels=c("All Judges","Judges with 1-4 Children"), #attempt at grouping columns
          keep = c("girls", "republican", "age", "religion", "woman", "race", "coefficients"),
          covariate.labels = c("1 Girl","2 Girls","3 Girls","4 Girls","5 Girls",
                               "At Least 1 Girl",	
                               "Republican","Age at Investiture","Catholic",
                               "Woman","African American","Hispanic",
                               "Constant"))
```
\newpage

"Weighted least squares results, gender cases only. Outcome is proportion of feminist votes.  Models 1--4 are for all judges, while Models 5--8 are for judges with 1--4 children.  (No judge among those with 1--4 children had four girls.) All models include fixed effects for number of children and use weights based on the number of cases heard by each judge."

THIS IS THE ONE WITH THE DATA THAT WE CHANGED UP! SO THIS IS THE CASE WHERE WE ONLY USE THE DATA FOR JUDGES WITH less than 14 CASES IN THE DATA

Good way to check the robustness of the results. Talk about what you find and why it is or is not intersting/expected

# Table 4: Weighted Least Squares Results, Gender-Related Cases Only
```{r, results="asis"}
########################################################
## Table 4: Core Results (WLS) 
########################################################

## Note from John: had to change as.factor(circuit.1) to as.factor(circuit_1), 
# because of the way that Zelig changed how they handle renaming columns
# with the same name

################ Results for all judges

judge_data_leq14 <- filter(judge_data, no_cases <= 14)

mod_1 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = judge_data_leq14, weights = judge_data_leq14$no_cases)

mod_2 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = judge_data_leq14, weights = judge_data_leq14$no_cases)

mod_3 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = judge_data_leq14, weights = judge_data_leq14$no_cases)

mod_4 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = judge_data_leq14, weights = judge_data_leq14$no_cases)
		
################ Results for judges between 1 and 4 children
	
mod_5 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = subset(judge_data_leq14, child < 5 & child > 0), weights = judge_data_leq14$no_cases[which(judge_data_leq14$child > 0 & judge_data_leq14$child < 5)])

mod_6 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = subset(judge_data_leq14, child < 5 & child > 0), weights = judge_data_leq14$no_cases[which(judge_data_leq14$child > 0 & judge_data_leq14$child < 5)])

mod_7 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = subset(judge_data_leq14, child < 5 & child > 0), weights = judge_data_leq14$no_cases[which(judge_data_leq14$child > 0 & judge_data_leq14$child < 5)])

mod_8 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = subset(judge_data_leq14, child < 5 & child > 0), weights = judge_data_leq14$no_cases[which(judge_data_leq14$child > 0 & judge_data_leq14$child < 5)])


cat("\\setcounter{table}{3}")
stargazer(mod_1, mod_2, mod_3, mod_4, mod_5, mod_6, mod_7, mod_8, 
          header = FALSE, style = "apsr", omit.stat = c("f","ser"),  font.size = "small",
          column.sep.width = "-8pt", digits = 2, 
          omit = c("circuit"), #line to omit descriptors
          dep.var.labels=c("All Judges","Judges with 1-4 Children"), #attempt at grouping columns
          keep = c("girls", "republican", "age", "religion", "woman", "race", "coefficients"),
          covariate.labels = c("1 Girl","2 Girls","3 Girls","4 Girls","5 Girls",
                               "At Least 1 Girl",	
                               "Republican","Age at Investiture","Catholic",
                               "Woman","African American","Hispanic",
                               "Constant"))
```


\newpage

"Weighted least squares results, gender cases only. Outcome is proportion of feminist votes.  Models 1--4 are for all judges, while Models 5--8 are for judges with 1--4 children.  (No judge among those with 1--4 children had four girls.) All models include fixed effects for number of children and use weights based on the number of cases heard by each judge."

THIS IS THE ONE WITH THE DATA THAT WE CHANGED UP! SO THIS IS THE CASE WHERE WE ONLY USE THE DATA FOR JUDGES WITH MORE THAN 5 CASES IN THE DATA



# Table 4: Weighted Least Squares Results, Gender-Related Cases Only
```{r, results="asis"}
########################################################
## Table 4: Core Results (WLS) 
########################################################

## Note from John: had to change as.factor(circuit.1) to as.factor(circuit_1), 
# because of the way that Zelig changed how they handle renaming columns
# with the same name

################ Results for all judges

judge_data_geq6 <- filter(judge_data, no_cases > 5)

mod_1 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = judge_data_geq6, weights = judge_data_geq6$no_cases)

mod_2 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = judge_data_geq6, weights = judge_data_geq6$no_cases)

mod_3 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = judge_data_geq6, weights = judge_data_geq6$no_cases)

mod_4 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = judge_data_geq6, weights = judge_data_geq6$no_cases)
		
################ Results for judges between 1 and 4 children
	
mod_5 <- lm(lib_vote_share ~ as.factor(girls) + as.factor(child), 
	data = subset(judge_data_geq6, child < 5 & child > 0), weights = judge_data_geq6$no_cases[which(judge_data_geq6$child > 0 & judge_data_geq6$child < 5)])

mod_6 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child), 
	data = subset(judge_data_geq6, child < 5 & child > 0), weights = judge_data_geq6$no_cases[which(judge_data_geq6$child > 0 & judge_data_geq6$child < 5)])

mod_7 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3), 
	data = subset(judge_data_geq6, child < 5 & child > 0), weights = judge_data_geq6$no_cases[which(judge_data_geq6$child > 0 & judge_data_geq6$child < 5)])

mod_8 <- lm(lib_vote_share ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit_1), 
	data = subset(judge_data_geq6, child < 5 & child > 0), weights = judge_data_geq6$no_cases[which(judge_data_geq6$child > 0 & judge_data_geq6$child < 5)])


cat("\\setcounter{table}{3}")
stargazer(mod_1, mod_2, mod_3, mod_4, mod_5, mod_6, mod_7, mod_8, 
          header = FALSE, style = "apsr", omit.stat = c("f","ser"),  font.size = "small",
          column.sep.width = "-8pt", digits = 2, 
          omit = c("circuit"), #line to omit descriptors
          dep.var.labels=c("All Judges","Judges with 1-4 Children"), #attempt at grouping columns
          keep = c("girls", "republican", "age", "religion", "woman", "race", "coefficients"),
          covariate.labels = c("1 Girl","2 Girls","3 Girls","4 Girls","5 Girls",
                               "At Least 1 Girl",	
                               "Republican","Age at Investiture","Catholic",
                               "Woman","African American","Hispanic",
                               "Constant"))
```

\newpage

# Table 5

One main critique of this table is that it treats every case as if it is identical, and tries to abstract away the details. This could not be further from the truth. It is possible that some judges do not hear some cases because the lower courts within the jurisdiction are more conservative/liberal, and so prevent reasonable cases from showing up in some areas, as opposed to others. There are other potential errors, including a small number of people who have heard a large number of cases - this means that there are going to be a lot of cases with the same inputs, and this can greatly affect the model. 

Good things to point out, fixed effects will account for a fair bit of this variation, but not all of it!

The whole argument for this paper is based off of the correctness of the variable progressive_vote, and this assumption appears to be questionable. The skewness of the number of cases makes it so that a small proportion of judges have heard a large number of the cases in the dataset. These prolific judges will result in a large number of cases that all have the same inputted demographic features, which will mean that the model can fit to this small portion of the population well and predict the overall outcomes of the lawsuits. 

Future work would check if there is a significant but spurious correlation between the number of cases in this dataset, the pattern of voting, and the pattern of demographic data. If these correlations existed, then the validity of the paper would be in question.

Great suggestion, this is something that could be done as a final project

\newpage

"Logit and ordered logit results, gender cases only. Outcome is whether judge in a case votes in a feminist direction (Columns 1--5) or in a conservative, moderate, or liberal direction (Column 6).  All models include fixed effects for total number of children and Columns 3--6 include circuit and year fixed effects. Column 5 additionally includes standard errors clustered at the case level

# Table 5: Logit and Ordered Logit Results, Gender-Related Cases Only
```{r, results="asis"}
#######################################################
## Table 5: Core Results (Case-Level)
#######################################################

# DO ALL EXCEPT COLUMN 6 OF THIS ONE

# it seems like Mark suggested that we do this one using the built in 
# packages, instead of using this Zelig code.


wom_cases <- case_data %>% filter(femplaintiff == 1, area %in% c("employment", "Title IX", "pregnancy", "abortion", "reproductive rights"), child < 5 & child > 0) %>% 
  mutate(area = factor(area, c("abortion", "employment", "pregnancy", "reproductive rights", "Title IX")))


mod_7 <- glm(progressive_vote ~ as.factor(girls) + as.factor(child), data = wom_cases, family = binomial)
mod_8 <- glm(progressive_vote ~ I(girls > 0) + as.factor(child), data = wom_cases, family = binomial)
mod_9 <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race ==3) + as.factor(circuit) + as.factor(year), data = wom_cases, family = binomial)
mod_10 <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = wom_cases, family = binomial)
my.out11 <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican + age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = wom_cases, family = binomial)

## Now: Calculating standard errors bootstrapped at the case level:
## Note: This takes about 10 minutes to run. 

## Grab the data for these two models
mod11 <- as.formula("~ progressive_vote + vote + girls +  child + republican +race + age + religion + woman + circuit + year + area + casename")

dat11 <- model.frame(mod11, data = subset(women_cases, child < 5 & child > 0))
dat11$casename <- as.character(dat11$casename)

## Create list of data.frames for each case for easy reference
casenames <- sort(unique(dat11$casename))
caselist <- lapply(casenames, function(x) dat11[which(dat11$casename == x),])
names(caselist) <- casenames


# in order to run the bootstrap algo, you need to uncomment out from "Running the bootstraps" to "End Bootstrap code here"

# otherwise you can just used the saved data

# # Running the bootstraps
# # Note that not all of the coefficients will be sampled in any given of the
# # bootstraps - this might result in some warnings form polr
# # (the ordered logit), but is not a problem for the results
# boots <- 1000
# b.star11 <- matrix(NA, ncol = length(list("(Intercept)",        "I(girls > 0)TRUE", "as.factor(child)2"   , "as.factor(child)3"   ,
# "as.factor(child)4"        ,          "republican"           ,
#  "age"                             ,   "I(religion == 4)TRUE"          ,
#  "woman"                ,              "I(race == 2)TRUE"             ,
#  "I(race == 3)TRUE"               ,    "as.factor(circuit)10"          ,
#  "as.factor(circuit)11"           ,    "as.factor(circuit)2"          ,
#  "as.factor(circuit)3"             ,   "as.factor(circuit)4"             ,
# "as.factor(circuit)5"              ,  "as.factor(circuit)6"            ,
#  "as.factor(circuit)7"               , "as.factor(circuit)8"           ,
#  "as.factor(circuit)9"      ,          "as.factor(circuit)DC"         ,
# "as.factor(year)1997"       ,         "as.factor(year)1998"         ,
#  "as.factor(year)1999"        ,        "as.factor(year)2000"        ,
#  "as.factor(year)2001"         ,       "as.factor(year)2002"       ,
# "as.factor(area)employment"    ,      "as.factor(area)pregnancy" ,
#  "as.factor(area)reproductive rights", "as.factor(area)Title IX" )), nrow = boots)
# colnames(b.star11) <- list("(Intercept)",        "I(girls > 0)TRUE", "as.factor(child)2"   , "as.factor(child)3"   ,
# "as.factor(child)4"        ,          "republican"           ,
#  "age"                             ,   "I(religion == 4)TRUE"          ,
#  "woman"                ,              "I(race == 2)TRUE"             ,
#  "I(race == 3)TRUE"               ,    "as.factor(circuit)10"          ,
#  "as.factor(circuit)11"           ,    "as.factor(circuit)2"          ,
#  "as.factor(circuit)3"             ,   "as.factor(circuit)4"             ,
# "as.factor(circuit)5"              ,  "as.factor(circuit)6"            ,
#  "as.factor(circuit)7"               , "as.factor(circuit)8"           ,
#  "as.factor(circuit)9"      ,          "as.factor(circuit)DC"         ,
# "as.factor(year)1997"       ,         "as.factor(year)1998"         ,
#  "as.factor(year)1999"        ,        "as.factor(year)2000"        ,
#  "as.factor(year)2001"         ,       "as.factor(year)2002"       ,
# "as.factor(area)employment"    ,      "as.factor(area)pregnancy" ,
#  "as.factor(area)reproductive rights", "as.factor(area)Title IX" )
# 
# set.seed(1234)
# for (b in 1:boots) {
# 	clust.sample <- sample(casenames, replace = TRUE)
# 	c.boot <- do.call(rbind,lapply(clust.sample,function(x) caselist[[x]]))
# 	out11.star <- glm(progressive_vote ~ I(girls>0) + as.factor(child) + republican
# 	+ age + I(religion == 4) + woman + I(race == 2) + I(race == 3) + as.factor(circuit) + as.factor(year) + as.factor(area), data = c.boot, family = binomial("logit"))
# 	  b.star11[b,names(out11.star$coef)] <- out11.star$coef
# 	  # b.star11[b,names(out11.star$coef)] <- out11.star$coef
# 		}
# bcse11 <- apply(b.star11, 2, sd, na.rm=TRUE)
# save(list=c("bcse11"), file = "bootstraps.RData")

## End bootstrap code here


## can re-load bootstraped data to avoid having to run previous code
load("bootstraps.RData")

# todo: fix the constant row of this table

## Replacing the normal SEs with the bootstrap SEs for the final Table 5
stargazer(mod_7, mod_8, mod_9, mod_10, my.out11, header = FALSE, font.size = "small", type = "latex",
	 style = "apsr", omit.stat = c("f","ser"), 
	 keep = c("girls", "republican", "age", "religion", "woman", "race", "area", "coefficients"),
	 covariate.labels = c("1 Girl","2 Girls","3 Girls","At Least 1 Girl","Republican","Age at Investiture","Catholic","Woman","African American","Hispanic", "Employment", "Pregnancy", "Reproductive", "Title IX"),
se = list(mod_7 = NULL, mod_8 = NULL, mod_9 = NULL, mod_10 = NULL, my.out11 = bcse11), digits = 2)



```

\newpage
# Table 6: omitted from results

# Table 7: Weighted Least Squares Results
```{r, results="asis"}
########################################################
## Table 7: Dividing Up the Sample
########################################################

## First, limiting sample space to only judges 
## with 1-4 kids 
#(there is only 1 judge with no girls conditional on 5 or more kids)

rep_means <- subset(rep_means, child < 5 & child > 0)
dem_means <- subset(dem_means, child < 5 & child >0)
men_means <- subset(men_means, child < 5 & child > 0)
women_means <- subset(women_means, child < 5 & child > 0)

## and then by case
rep_cases <- subset(women_cases, child < 5 & child > 0 & republican == 1)
dem_cases <- subset(women_cases, child < 5 & child > 0 & republican == 0)
men_cases <- subset(women_cases, woman == 0)
womyn_cases <- subset(women_cases, woman == 1)


################ Party

mod_PARTY <- lm(lib_vote_share ~ I(girls > 0)*republican + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

## for republicans

mod_REP <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = rep_means, weights = rep_means$no_cases)

## for democrats

mod_DEM <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = dem_means, weights = dem_means$no_cases)

################ Gender

## for men
	
mod_GENDER <- lm(lib_vote_share ~ I(girls > 0)*woman + as.factor(child), 
	data = judge_data, weights = judge_data$no_cases)

## for men
mod_MEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = men_means, weights = men_means$no_cases)

## for women
mod_WOMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = women_means, weights = women_means$no_cases)

mod_REPMEN <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = subset(men_means, republican == 1), weights = men_means$no_cases[which(men_means$republican == 1)])

cat("\\setcounter{table}{6}")
stargazer(mod_REP, mod_DEM, mod_MEN, mod_WOMEN, mod_REPMEN,
	style = "ajps", header = FALSE, omit.stat = c("f","ser"), dep.var.labels = "Share of Votes in Feminist Direction", digits = 2, covariate.labels = c("At Least 1 Girl", "2 Children", "3 Children", "4 Children","Constant"), title = "Weighted least squares results. Outcome is judges' proportion of feminist votes on gender-related cases. All models include fixed effects for total number of children and use weights based on the number of cases heard by each judge.", label = "t:results_party")

```

\newpage
# Table 8
```{r, results="asis"}


########################################################
## Table 8: Judges with 0 or 1 child
########################################################

## Including people who have zero children as a control 
## suggested by AJPS editor 
## (Note: Caution against making inferences on effect of
## daughters among people with 0 children)

mod_12 <- lm(lib_vote_share ~ I(girls > 0) + as.factor(child), 
	data = subset(judge_data, child < 2), 
		weights = judge_data$no_cases[which(judge_data$child < 2)])
# summary(my.out12)

mod_13 <- lm(lib_vote_share ~ I(girls > 0), 
	data = subset(judge_data, child == 1), 
		weights = judge_data$no_cases[which(judge_data$child == 1)])
# summary(my.out13)

## and then controlling for rep or dem:

mod_14 <- lm(lib_vote_share ~ I(girls > 0) + I(republican==1), 
	data = subset(judge_data, child == 1), 
		weights = judge_data$no_cases[which(judge_data$child == 1)])
# summary(my.out14)


stargazer(mod_12, mod_13, mod_14, header = FALSE, 
	style = "ajps", omit.stat = c("f","ser"), dep.var.labels = "Liberal Judge-Vote",
	covariate.labels = c("1 Girl", "1 Child", "Republican", "Constant"))
```
\newpage
# Table 9: Proportion of Girls (Conditional on Number of Children) for U.S. Courts of Appeals Judges Participating in Gender-Related Cases, 1996-2002
```{r, results="asis"}

########################################################
## Table 9: Distribution of gender-related cases
########################################################


## just republicans:
rep_means <- subset(judge_data, republican == 1)

## just democrats
dem_means <- subset(judge_data, republican == 0)



aa <- table(dem_means$child, dem_means$girl)

bb <- table(rep_means$child, rep_means$girl)


aa_1 <- prop.table(table(dem_means$child, dem_means$girl),1)
bb_1 <- prop.table(table(rep_means$child, rep_means$girl),1)

colnames(aa_1) <- c("0 Girls", "1 Girl", "2 Girls", "3 Girls", "4 Girls", "5 Girls")

colnames(bb_1) <- c("0 Girls", "1 Girl", "2 Girls", "3 Girls", "4 Girls")

xtable(cbind(aa_1, bb_1))
```

# REMOVED TABLES:
# Table 1: Number of Children and Girls for U.S. Courts of Appeals Judges Participating in Gender-Related Cases, 1996-2002
```{r, results="asis"}
######################################################
## Table 1: Number of children and girls
######################################################

# Table 1: Number of Children and Girls for U.S. Courts of Appeals Judges 
#          Participating in Gender-Related Cases, 1996-2002
# Here we are keeping the # of children, # of girls, & party affiliation and
# building a count table. Additionally, here the party name is recoded to be
# more friendly to a reader of the table ("Republicans" and "Democrats")
t1 <- select(judge_data,
              child, girls, republican) %>% 
  filter(child < 10, girls < 10) %>% 
  mutate(party = ifelse(1 == republican, "Republicans", "Democrats"))


# Number of Children portion of the table
t1_child <- t1 %>% 
  count(party, child) %>% 
  spread(child, n) %>% 
  adorn_totals("col")

# Number of Girls portion of the table
t1_girls <- t1 %>% 
  count(party, girls) %>% 
  spread(girls, n) %>% 
  adorn_totals("col")

# Binding the rows to create one table with girls and children
# column_spec is a function that adds the row with the total counts
t1_combined <- bind_rows(t1_child, t1_girls)
colnames(t1_combined) <- c("Count", "0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "N")
t1_combined %>% 
  kable("latex", booktabs = TRUE, col.names = ) %>% kable_styling(position = "center") %>% 
  column_spec(1, bold = TRUE) %>% 
  group_rows("Number of Children", 1, 2, bold = TRUE) %>% 
  group_rows("Number of Girls", 3, 4, hline_before = TRUE)
```

## Figure 1: Distribution of the Proportion of Cases Decided in a Feminist Direction out of All Gender-Related Cases Decided, 1996-2002
```{r}
#######################################################
## Figure 1
########################################################

plot(density(judge_data$lib_vote_share), 
	xlim = c(-.4,1.4), ylim = c(0,2.5),
	ylab = "", xlab = "Proportion of Cases Decided in a Feminist Direction", 
	yaxt = "n", 
	bty = "n", 
	main = "",
	col = "black", lwd = 2)
lines(density(rep_means$lib_vote_share), 
	col = "firebrick", lwd = 2, lty  = 2)
lines(density(dem_means$lib_vote_share), 
	col = "dodgerblue", lwd = 2, lty  = 3)
abline(v = .5, col = "grey50", lty = 2)
text(x = .5, y = 2.4, "Less Feminist", col = "grey50", pos = 2, cex = 0.9)
text(x = .5, y = 2.4, "More Feminist", col = "grey50", pos = 4, cex = 0.9)
text(x = .25, y = 1.7, "Republicans", pos = 2, cex = 0.9)
text(x = .7, y = 1, "Democrats", pos = 4, cex = 0.9)
text(x = .075, y = .6, "All", pos = 4, cex = 0.9)

```

Moving forward, we'll definitely want bibliographies for replications

This is a great first replication. It would be helpful to me if the tables/figures were kept in the same order as they appear in the paper, but everything looks professionally done, your comments are clear and detailed, and code efficient and elegannt Great work!
